Adolescent well-being in the digital age

### 2022-01-10 00-clean.qmd
Add mock gwp data

```{r}
# Create if doesn't exist
gwp_mock_path <- "data-raw/gwp-MOCK.rds"
if (!file.exists(gwp_mock_path)) {
  distinct(gwp, outcome, country, year, sex, age) %>% 
    mutate(
      se = rnorm(
        nrow(.), 
        mean(gwp$se, na.rm = TRUE), 
        sd(gwp$se, na.rm = TRUE)
      ),
      val = rnorm(
        nrow(.), 
        mean(gwp$val, na.rm = TRUE), 
        sd(gwp$val, na.rm = TRUE)
      )
    ) %>% 
    write_rds(gwp_mock_path, compress = "xz")
}
# Load if actual data doesn't exist
if (!dir.exists("data-raw/Gallup")) {
  cat("Using synthetic GWP data.")
  gwp <- read_rds(gwp_mock_path)
} else {
  cat("Using actual GWP data.")
}
```

>>>>

```{r}
# Create if doesn't exist
gwp_mock_path <- "data-raw/gwp-MOCK.rds"
if (!file.exists(gwp_mock_path)) {
  set.seed(101010)
  distinct(gwp, outcome, country, year, sex, age) %>% 
    mutate(
      se = rnorm(
        nrow(.), 
        mean(gwp$se, na.rm = TRUE), 
        sd(gwp$se, na.rm = TRUE)
      ),
      val = rnorm(
        nrow(.), 
        mean(gwp$val, na.rm = TRUE), 
        sd(gwp$val, na.rm = TRUE)
      )
    ) %>% 
    write_rds(gwp_mock_path, compress = "xz")
}
# Load if actual data doesn't exist
if (!dir.exists("data-raw/Gallup")) {
  cat("Using synthetic GWP data.")
  gwp <- read_rds(gwp_mock_path)
} else {
  cat("Using actual GWP data.")
}
```
